## Homework 4

<!--
Remember you can use the example4.Rmd or other files to find examples
of the codes you'll need to use to complete this assignment. I strongly
urge you to copy and paste relevant code that you know works from my
examples or instructions and then edit that code so you're working
with the appropriate variables for the homework.
-->

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->

<!--
Read in the homework4.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
-->

The first step is to read in the data.
```{r}
dat<-read.csv("homework4.csv")
```

<!--
Check the structure of the data.
-->
The next step is to check out the structure
```{r}
str(dat)
```

<!--
Create a table that shows how many people fell into each category.
-->
Now I'll create a table that shows how many people fell into each
category of agreement and condition.
```{r}
table(dat$agreement, dat$condition)
```


<!--
Perform a chi-square test to determine whether or not the experimental
conditions and agreement with a statement are independent or related.
Also, interpret the results of your test and provide a a statistical
statement that supports your interpretation. As there's no way to
insert the chi-square symbol, you can just use chi-square instead
(see example4.Rmd).
-->
Now we'll run a Chi-square test to determine whether the experimental conditions and agreement for a statement are related.
```{r}
chisq.test(dat$agreement,dat$condition)
```
According to the results of the Chi-square test, the experimental manipulation didn't affect how much people agreed with the statement, X^2(1) = 1.2, p = .26.