## Homework 5

<!--
Set the working directory.
No Rchunk is needed to accomplish this.
-->



<!--
Read in the homework5.csv data. For each of the following steps you
should preface your R commands with some plain English explanation.
The data are fabricated and include the number of words per minute
that people can type when listening to no music and when listening
to heavy metal.
-->
The first step is to read in the data.
```{r}
dat<-read.csv("homework5.csv")
```


<!--
Check the structure of the data.
-->
The next step is to check out the structure
```{r}
str(dat)
```
As we can see dat is a data frame with two variables: music and wpm.

<!--
Find the mean words per minute for the two groups.
-->

```{r}
mean(dat$wpm[dat$music=="metal"])
mean(dat$wpm[dat$music=="none"])
```
By looking at the means it appears that the metal group
had more words per minute than the none group.
<!--
Run an independent t-test to determine if the mean wpm for the
no music group is different from the mean wpm from heavy metal
group. Interpret the results of your analysis after you run it.
-->
Now I'll perform an independent t-test to see if my intuition was
correct.
```{r}
t.test(dat$wpm[dat$music=="none"],
       dat$wpn[dat$music=="metal"],
       var.equal=TRUE)
```
Examining the results of our t-test we can see that 
the experimental group performed the task quicker than individuals
in the control group, t(31) = 26, p = 2.2e-16.
<!--
Run another independent t-test with the alternative hypothesis that
the heavy metal group types faster than the no music group. Interpret
the results of your analyses.
-->
Now, I'll run an independent t-test with the alternative hypothesis
that the heavy metal group types more than the no music group.
```{r}
t.test(dat$wpm[dat$music=="none"],
       dat$wpm[dat$music=="metal"],
       var.equal=TRUE,
       alternative="greater")
```
Examining the results of our t-test we can see that individuals in
the heavy metal group typed more words than the no music group, t(62) = -2.3, p = 0.9885.

<!--
Create a bar graph of the data.
-->
In order to create a figure of the data, I need to load the
ggplot2, gplots, and dplyr libraries.
```{r}
library(ggplot2)
library(gplots)
library(dplyr)
```
Next I need to use dplyr to summarize the data and find the means and
standard errors of the means for the different groups.
```{r}
temp<-dat%>%group_by(music)%>%
  summarize(means=mean(wpm), sems=sd(wpm)/sqrt(length(wpm)))
```
Armed with the summarized data I can now create a figure of the data.
```{r}
f<-ggplot(temp,aes(x=factor(music),y=means))+
  geom_bar(stat="identity", color="black",
           fill=c("deepskyblue2", "deeppink"))+
  geom_errorbar(aes(ymax=means+sems,
                    ymin=means-sems),
                width=.2)+
  ggtitle("Response Times For the Groups")+
  labs(x="Group", y="Response Time (ms)")+
  scale_x_discrete(breaks=c("metal","none"),
                   labels=c("metal","none"))+
  theme(plot.title=element_text(size=15,
                                face="bold",
                                vjust=.5))+
  theme(axis.title.x=element_text(size=12,
                                  face="bold",
                                  vjust=-.25))+
  theme(axis.title.y=element_text(size=12,
                                  face="bold",
                                  vjust=.25))+
  theme(axis.text.x=element_text(size=10,
                                 face="bold",
                                 color="black"))+
  theme(axis.text.y=element_text(size=10,
                                 face="bold",
                                 color="black"))+
  coord_cartesian(ylim=c(min(temp$means)-2*max(temp$sems),
                         max(temp$means)+2*max(temp$sems)))+
  theme(panel.border=element_blank(),
        axis.line=element_line())+
  theme(panel.grid.major.x=element_blank())+
  theme(panel.grid.major.y=element_line(color="darkgrey"))+
  theme(panel.grid.minor.y=element_blank())
f
```
<!--
Conduct and interpret a two-tailed paired t-test on the data.
-->
Now I will conduct a two-tailed paired t-test.
```{r}
t.test(dat$wpm[dat$music=="none"],
       dat$wpm[dat$music=="metal"],
       var.equal=TRUE,
       paired=TRUE)
```
Individuals in the heavy metal condition completed the task more
quickly than individuals in the no music condition, t(31) = -12.2,
p < 2.51e-13.
